---
title: "Revisitando uma visualização"
output: html_notebook
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(htmlwidgets)
library(here)
theme_set(theme_bw())
```


```{r warning=FALSE}
dados = read_csv(here("data/series_from_imdb.csv"), 
                    progress = FALSE,
                    col_types = cols(.default = col_double(), 
                                     series_name = col_character(), 
                                     episode = col_character(), 
                                     url = col_character(),
                                     season = col_character())) %>% 
                                    filter(series_name %in% c("Dexter", "How I Met Your Mother")) 

dexter <- dados %>% filter(series_name == "Dexter") 
himym <- dados %>% filter(series_name == "How I Met Your Mother") 

```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

